Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-07-26 paper.Rnw
updated based on limeaid updates

# Extract the explanations from the default lime application
# for the prediction of interest only
sine_poi_lime_default <- sine_lime_default %>%
  filter(case == sine_poi %>% pull(case)) %>%
  mutate(case = c("Prediction of Interest", "Prediction of Interest"))

@@

Figure ... provides example explanation scatterplots for each feature in the default LIME explanation for the \data \ prediction of interest indicated in Figure \ref{fig:sine-plot-data}. \kgc{Need to updated limeaid to create this plot and then add figure here.}

@@

\begin{figure}[!thp]
<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.25, warning = FALSE>>=

>>>>

# Extract the explanations from the default lime application
# for the prediction of interest only
sine_poi_lime_default <- sine_lime_default %>%
  filter(case == sine_poi %>% pull(case)) %>%
  mutate(case = c("Prediction of Interest", "Prediction of Interest"))
@

@@

Figure \ref{fig:sine-expl-scat-density} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.

\begin{figure*}[!thp]
<<sine-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 4.5, fig.align = "center">>=
plot_explain_scatter(
  sine_lime_explain$explain %>%
    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
  alpha = 0.75, title.opt = FALSE
) + 
  theme_bw(base_family = "Times") +
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.placement = "outside")
@
\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
\label{fig:sine-expl-scat-density}
\end{figure*}

@@

\begin{figure}[!thp]
<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 4, warning = FALSE>>=
